Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-12 journal/content.tex
Work on conclusion

* Some success factors and challenges relate

* Some success factors and challenges are ``symmetrical'', so that lack of some
  factor is a challenge, but availability of it provides success

@@

% Different organizations

* It is difficult to distinguish between team and organization. In most cases
  when talking about teams it refers to a handful of people familiar to each
  other. However, in some cases it was evident that an entire department was
  referred to as a team.

* Projects and organizations. How to distinguish between a separate adoption in
  the beginning of each project, and an organization wide adoption.

% Other ?

* System development life cycle ?? -- There are inevitably other areas than
  development of increments, even in an agile process

* How do transformations fit within Kotter's 8 step process?

* A qualitative interpretation requires much text. Therefore the results got
  long. See ``Meta-ethnography''.

>>>>

It is evident in the results that some success factors and challenges relate.
Some success factors and challenges are complementary, so that lack of some
factor is a challenge, but availability of it provides success.
A particular complementary relationship could be observed in use of training

@@

% Different organizations
% 
% * A recommendation for further research
%
% * It is difficult to distinguish between team and organization. In most cases
%   when talking about teams it refers to a handful of people familiar to each
%   other. However, in some cases it was evident that an entire department was
%   referred to as a team.
% 
% * Projects and organizations. How to distinguish between a separate adoption in
%   the beginning of each project, and an organization wide adoption.

% Other ?
% 
% * System development life cycle ?? -- There are inevitably other areas than
%   development of increments, even in an agile process
% 
% * How do transformations fit within Kotter's 8 step process?
% 
% * A qualitative interpretation requires much text. Therefore the results got
%   long. See ``Meta-ethnography''.
